Global Optimization of an Analog Method by Means of Genetic Algorithms

### 2016-09-06 Genetic algorithms - MWR/template.tex
Adding results of the confidence interval analysis.

In order to evaluate a combination of operators/options, 10 optimizations per configuration of GAs were processed. With all assessed combinations of GAs options, 21,630 optimizations were performed on an Intel Xeon based HPC cluster with 96 cpu, running Linux RedHat. Such assessment is not possible on the whole archive length, and had to be performed on a reduced period (5 years). The total resources needed for this comparison amounts to 229,539 h/cpu (26.2 years). One should remember that these intensive resources were needed in order to assess multiple combinations of GAs options in order to provide recommendations. Based on these, applying GAs to optimize AMs require some computational power, but not as much (the time needed is function of the archive length, the population number, the other GAs options, and the complexity of the AM to optimize).

@@

\subsection{Success of the approach}

@@

>>>>

In order to evaluate a combination of operators/options, 10 optimizations per configuration of GAs were processed. With all assessed combinations of GAs options, 21,630 optimizations were performed on an Intel Xeon based HPC cluster with 96 cpu, running Linux RedHat. Such assessment is not possible on the whole archive length, and had to be performed on a reduced calibration period : 5 years, from 1998 to 2002, but looking for analog dates on a 48 years period (1961-2008). The total resources needed for this comparison amounts to 229,539 h/cpu (26.2 years). One should remember that these intensive resources were needed in order to assess multiple combinations of GAs options in order to provide recommendations. Based on these, applying GAs to optimize AMs require some computational power, but not as much (the time needed is function of the archive length, the population number, the other GAs options, and the complexity of the AM to optimize).

@@

\subsection{Convergence}

@@

\subsection{Illustration of application}

Ref: 95\%   ( 0.2921,  0.3494 )  
Optimized: 95\%   ( 0.3521,  0.4011 )
